### 2023-07-20 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
Update multicomponent_vesicles.tex
very minor changes

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Validation}
\label{sec:validation}
We validate the new bending model~\eqref{eqn:tanhBending} by reproducing
the dynamics reported in the literature. Figure~\ref{fig:treading} shows
a phase treading (top) ajnd a tank treading (bottom) multicomponent
vesicle in an unconfined shear flow. These simulations align with the
results reported by~\citet{liu-mar-li-vee-low2017} (cf.~Figures 3 and
4).
\begin{figure}[H]
  \centering
  \includegraphics[width=0.9\columnwidth]{figures/shearTreading.pdf}
%  \subfigimg[width=\columnwidth, trim ={5.5cm 1.5cm 4cm 0},clip]{(a)}{figures/Fig4a.pdf}
%  \subfigimg[width=\columnwidth, trim ={5.5cm 1.5cm 4cm 0},clip]{(b)}{figures/Fig4b.pdf}
  \caption{\label{fig:treading} \small A multicomponent vesicle in a
  linear shear flow undergoes phase-treading (top) and tank-treading
  (bottom) with the new bending model~\eqref{eqn:tanhBending}. The red
  region is stiff and the blue region is floppy. The simulations
  qualitatively agree with the results presented
  by~\citet{liu-mar-li-vee-low2017}.}
\end{figure}

@@

A difference between the size of the top and lubrication layers
indicates that the vesicle is off-centered from the center of the
channel, and this results in tank-treading behavior~\cite{aga-bir2020}.
To determine if a vesicle is tank-treading, we calculate the tangential
velocity at several points on $\gamma$, and if this value is constant,
this is the tank-treading velocity.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:results}Hydrodynamics of a multicomponent vesicle
under strong confinement}
We consider both a single-component and a multicomponent vesicle
suspended in two geometries: a closely-fitting geometry (stenosis) and a
geometry that slowly contracts to a narrow neck and then quickly widens
(contracting). We considered a semipermeable vesicle suspended in these
same geometries in our previous work~\cite{qua-gan-you2021}. All the
multicomponent examples have floppy-to-stiff ratio $\beta = 10^{-1}$.
For the single-component case, we consider two bending stiffnesses:
$b(u) = 1$ and $b(u) = 0.55$ which is the average bending stiffness of a
multicomponent vesicle whose stiff and floppy regions have the same
area. Throughout this section we plot the position of the vesicle in
terms of the $x$-coordinate of its center of mass. For the stenosed
geometry in Section~\ref{subsec:Stenosis}, the narrow region begins at
$x=-15$ and ends at $x=15$. For the contracting geometry in
Section~\ref{subsec:Contraction}, the geometry begins to narrow at $x=4$
and reaches its narrowest point at $x=15$.

@@

We start by considering a vesicle with reduced area $\alpha = 0.6$
passing through stenosis with a capillary number $Ca = 0.25$.
Figure~\ref{fig:RA6} shows six time steps of a (a) stiff
single-component (b) floppy single-component, and (c) multicomponent
vesicle. The initial lipid distribution of the multicomponent is random.
In all plots, the color is the dimensionless bending modulus of the
multicomponent vesicle that remains bounded in $[0.1,1]$ by using the
new bending modulus~\eqref{eqn:tanhBending}. A single Lagrangian point
is included to visualize any tank-treading behavior. There are slight
differences between the three cases, with the most noticeable being that
the multicomponent vesicle has higher curvature in the floppy region.
However, in general, there is little difference between these cases,
partially because these vesicles have a large reduced area. With the
current setup, an elliptical vesicle with reduced area greater than
$\alpha = 0.8$ cannot fit through the closely-fitting geometry.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Validation}
\label{sec:validation}
We validate the new bending model~\eqref{eqn:tanhBending} by reproducing
the dynamics reported in the literature. Figure~\ref{fig:treading} shows
a phase treading (top) ajnd a tank treading (bottom) multicomponent
vesicle in an unconfined shear flow. These simulations align with the
results reported by~\citet{liu-mar-li-vee-low2017} (cf.~Figure 3).
\begin{figure}[H]
  \centering
  \includegraphics[width=0.9\columnwidth]{figures/shearTreading.pdf}
%  \subfigimg[width=\columnwidth, trim ={5.5cm 1.5cm 4cm 0},clip]{(a)}{figures/Fig4a.pdf}
%  \subfigimg[width=\columnwidth, trim ={5.5cm 1.5cm 4cm 0},clip]{(b)}{figures/Fig4b.pdf}
  \caption{\label{fig:treading} \small A multicomponent vesicle in a
  linear shear flow undergoes phase-treading (top) and tank-treading
  (bottom) with the new bending model~\eqref{eqn:tanhBending}. The red
  region is stiff and the blue region is floppy. The simulations
  qualitatively agree with the results presented
  by~\citet{liu-mar-li-vee-low2017}.}
\end{figure}

@@

A difference between the size of the top and bottom lubrication layers
indicates that the vesicle %is off-centered 
has deviated from the center of the
channel, and this results in tank-treading behavior~\cite{aga-bir2020}.
To determine if a vesicle is tank-treading, we calculate the tangential
velocity at several points on $\gamma$, and if this value is constant,
this is the tank-treading velocity.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:results}Hydrodynamics of a multicomponent vesicle
under strong confinement}
We consider both a single-component and a multicomponent vesicle
suspended in two geometries: a closely-fitting geometry (stenosis) and a
geometry that slowly contracts to a narrow neck and then quickly widens
(contracting). We considered a semipermeable vesicle suspended in these
same geometries in our previous work~\cite{qua-gan-you2021}. All the
multicomponent examples have floppy-to-stiff ratio $\beta = 10^{-1}$.
For the single-component case, we consider two bending stiffnesses:
$b(u) = 1$ and $b(u) = 0.55$. % which is the average bending stiffness of a multicomponent vesicle whose stiff and floppy regions have the same area. 
The latter value represents the average bending stiffness of a multicomponent vesicle, where the stiff and floppy regions have the same area. Throughout this section we plot the position of the vesicle in terms of the $x$-coordinate of its center of mass. For the stenosed
geometry in Section~\ref{subsec:Stenosis}, the narrow region begins at
$x=-15$ and ends at $x=15$. For the contracting geometry in
Section~\ref{subsec:Contraction}, the geometry begins to narrow at $x=4$
and reaches its narrowest point at $x=15$.

@@

We start by considering a vesicle with reduced area $\alpha = 0.6$
passing through stenosis with a capillary number $Ca = 0.25$.
Figure~\ref{fig:RA6} shows six time steps of a (a) stiff
single-component (b) floppy single-component, and (c) multicomponent
vesicle. The initial lipid distribution of the multicomponent vesicle is random.
In all plots, the color is the dimensionless bending modulus of the
multicomponent vesicle that remains bounded in $[0.1,1]$ by using the
new bending modulus~\eqref{eqn:tanhBending}. A single Lagrangian point
is included to visualize any tank-treading behavior. There are slight
differences between the three cases, with the most noticeable being that
the multicomponent vesicle has higher curvature in the floppy region.
However, in general, there is little difference between these cases,
partially because these vesicles have a large reduced area. With the
current setup, an elliptical vesicle with reduced area greater than
$\alpha = 0.8$ cannot fit through the closely-fitting geometry.
